%-------------------------
% Muhammed Shabeer TM - Senior Flutter Developer
% Built from user's original resume - no invented content
% Targeted for Google / top product companies
% ATS-friendly + professional design
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[
  hidelinks,
  pdfborder={0 0 0},
  pdfhighlight=/N
]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\footskip}{14pt}

% Margins (proven to fit on one page)
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-1.0in}
\addtolength{\textheight}{2.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{2pt}\large\bfseries
}{}{0em}{}[\vspace{-2pt}\titlerule\vspace{2pt}]
\titlespacing*{\section}{0pt}{4pt}{2pt}

% ATS-readable PDF
\pdfgentounicode=1
\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
  pdfhighlight=/N
}

\newcommand{\role}[4]{
  \vspace{2pt}
  \noindent\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    #3 & #4 \\
  \end{tabular*}
  \vspace{-6pt}
}

\newcommand{\project}[2]{
  \noindent\textbf{#1} \hspace{2pt}\textemdash\hspace{2pt} #2
  \vspace{1pt}
}

\setlist[itemize]{leftmargin=0.2in, itemsep=0pt, topsep=1pt, parsep=0pt}

\begin{document}

\mbox{}\vspace{15pt}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Muhammed Shabeer TM}\\[4pt]
    {\small Senior Flutter Developer}\\[6pt]
    {\small
    \faPhone*\ +91 9567200188 \quad
    \faEnvelope\ muhmmdshabeer@gmail.com \quad
    \faLinkedin\ LinkedIn: linkedin.com/in/muhammed-shabeer-tm-55271018b\\[2pt]
    \faGlobe\ Portfolio: shabeer.pages.dev \quad
    \faGithub\ GitHub: github.com/meahdev \quad
    \faMedium\ Medium: medium.com/@muhmmdshabeer
    }
\end{center}

\vspace{-4pt}

%-----------EXPERIENCE-----------
\section*{Experience}

\role{Heroic Cybersecurity}{Jun 2025 -- May 2026}{Senior Flutter Developer}{Remote (US)}
\begin{itemize}
  \item Led the complete revamp of HEROIC Guardian using Clean Architecture and BLoC, improving scalability, modularity, and maintainability.
  \item Owned the full product lifecycle of HEROIC Guardian across Android and iOS, including analytics, crash monitoring, user reviews, retention, and app store optimization; grew downloads from 200 to nearly 10,000 with steady ongoing growth.
  \item Engineered the full IAP subscription lifecycle (validation, restoration, receipt handling), reducing subscription failures by 35\%.
  \item Implemented Firebase Crashlytics and Analytics, reducing crash rate by 28\% and improving onboarding insights.
  \item Architected a Windows security agent in Flutter and Go with secure IPC and JWT authentication for real-time osquery telemetry.
  \item Led mobile performance monitoring via Play Console and Firebase, delivering weekly KPI reports and A/B testing insights.
  \item Led the complete UX revamp of InternetGuard VPN and reduced ANRs by 40\%, raising Play Store rating to 4.0+ and contributing to download growth from 1M to 1.5M+.
\end{itemize}

\role{HiFX IT \& Media Services}{Sep 2023 -- Dec 2024}{Senior Flutter Developer}{Kochi, India}
\begin{itemize}
  \item Architected and developed a Single Sign-On (SSO) solution for Manorama applications serving 10M+ users with Google and Apple login integration.
  \item Led migration of native Android and iOS app Hello Address to Flutter, unifying codebases and improving development velocity and maintainability.
  \item Applied Riverpod within a Domain-Driven Design (DDD) architecture to improve scalability, modularity, and separation of concerns.
  \item Automated CI/CD pipelines using Jenkins, reducing release deployment time by 60\% and eliminating manual release errors.
  \item Integrated Stripe and native in-app payments, increasing subscription conversion rate by 22\% and ensuring PCI-compliant transactions.
  \item Established unit, widget, and integration test coverage to 75\%, reducing post-release defects by 30\%.
\end{itemize}

\role{Seeroo IT Solutions}{Dec 2019 -- Aug 2023}{Flutter Developer}{Kochi, India}
\begin{itemize}
  \item Built and scaled 5+ production-grade Flutter applications using BLoC, Provider, and GetX within MVVM and Clean Architecture patterns.
  \item Reduced application crashes by 90\% through debugging, profiling, and performance optimization.
  \item Integrated secure payment gateways (Freecharge, Payfort) and Firebase Cloud Messaging (FCM) for real-time engagement.
  \item Engineered advanced geolocation modules (reverse geocoding, background tracking), improving location accuracy by 25\% and reducing API response latency.
  \item Integrated AWS Amplify services (Cognito, Lambda) for secure authentication and scalable backend communication.
\end{itemize}

%-----------SHIPPED PRODUCTS----------
\section*{Shipped Products}
\vspace{2pt}
\project{HEROIC Guardian}{Breach Monitoring \& Cybersecurity Mobile Application \quad \textcolor{blue}{Android} \quad \textcolor{blue}{iOS}}

\project{InternetGuard}{VPN Firewall \& Privacy Protection Application \quad \textcolor{blue}{Android}}

\project{Hello Address}{Real Estate Mobile Application \quad \textcolor{blue}{Android} \quad \textcolor{blue}{iOS}}

\project{BuddyGuru}{Music \& Arts Social Platform \quad \textcolor{blue}{Android} \quad \textcolor{blue}{iOS}}

\project{Unidoc}{Healthcare Appointment Scheduling Application \quad \textcolor{blue}{Android} \quad \textcolor{blue}{iOS}}

%-----------TECHNICAL SKILLS----------
\section*{Technical Skills}
\vspace{2pt}
\noindent
\textbf{Languages} \quad Dart, Go, Kotlin, Java, Swift \\
\textbf{Frameworks} \quad Flutter \\
\textbf{Architecture} \quad Clean Architecture, MVVM, DDD, BLoC, Riverpod, Provider, GetX \\
\textbf{Backend \& Cloud} \quad REST APIs, Firebase, AWS Amplify (Cognito, Lambda) \\
\textbf{Payments} \quad Stripe, In-App Purchases \\
\textbf{DevOps \& Tools} \quad Jenkins, Codemagic, Git, GitHub, GitLab, Android Studio, Xcode, VS Code, Postman \\
\textbf{Practice} \quad Agile, Scrum, Jira

%-----------EDUCATION-----------
\section*{Education}
\vspace{2pt}
\noindent\textbf{Bachelor of Science in Computer Science} \hspace{2pt}\textemdash\hspace{2pt} Calicut University, Kerala \hfill 2014 -- 2017

\end{document}
